---
title: "TIMs Evolution"
author: "Ahmed Aquib"
date: "2025-08-14"
output:
  powerpoint_presentation: default
  ioslides_presentation: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## TIM4

-   TIMD4_HUMAN
-   T-cell immunoglobulin and mucin domain-containing protein 4
-   378 AA in length
-   PS binding receptor expressed on APCs

## TIM4 Domain and Evolution

-   Igv Domain containing protein
-   Orthologs with significant homology present in vertebrates (42%
    Homology with Zebra Fish timd4; Alliance of Genome)
-   No significant homology with invertebrates (C. elegans, and
    Drosophila; Blast)
-   Igv Domain containing proteins are present in invertebrates

## Multiple Sequence Analysis – Species List

**Great Apes:** *Homo sapiens* – Human; *Pan troglodytes* – Common
chimpanzee; *Pan paniscus* – Bonobo; *Gorilla gorilla* – Western
gorilla; *Pongo abelii* – Sumatran orangutan; *Nomascus leucogenys* –
Northern white-cheeked gibbon\
**Old World Monkeys:** *Macaca mulatta* – Rhesus macaque; *Papio anubis*
– Olive baboon\
**New World Monkeys:** *Cebus capucinus* – White-faced capuchin;
*Saimiri boliviensis* – Bolivian squirrel monkey; *Callithrix jacchus* –
Common marmoset\
**Strepsirrhines:** *Lemur catta* – Ring-tailed lemur

## Molecular

```{r cars, echo = TRUE}

```

## Slide with Plot

```{r pressure}

```
